Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-18 paper/uist_2016/paper.tex
add a minor note about mixed-methods

@@

@@

\subsection{Procedure}
Participants underwent a two-week tracking period followed by a user study which investigated the memorability, believability, and desirability of the Rewinds produced from the two weeks of location data.

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{Rewind-seasons2}
	\caption{Plantation is classified using HSV color space, and the HSV values were adjusted to reflect seasonal changes}
	\label{fig:season}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{Rewind-weather}
	\caption{Meterological attributes are depicted using JavaScript canvas painting and animation}
	\label{fig:weather}
\end{figure*}

@@

\subsection{Procedure}
Participants underwent a two-week tracking period followed by a mixed-methods user study which investigated the memorability, believability, and desirability of the Rewinds produced from the two weeks of location data.

@@
